Decompositions of congruence subgroups of Chevalley groups

### 2015-10-09 paper.tex
Scrapper explicit formulae for root unipotents

The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$ as follows. Blah-blah-blah
\textbf{TODO: Write a passage about this} %TODO:

@@

Although it is possible to fix signs of the action constants in the statement of \cref{lemma:Matsumoto} in the general situation (see~\cite{V08}),
for our purposes it suffices to do that only for classical groups in their natural representations.

\begin{rem}
Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ of a classical group such that $\lambda_1-\lambda_2\in \Phi$.
In this situation it will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ (for some choice of $\lambda_1,\lambda_2$) instead of $x_{\lambda_1-\lambda_2}(\xi)$.
For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$. \end{rem}
For classical groups there is a standard way to fix the signs.
In case $\Phi=\rC_\ell$ the long and short root unipotents are
\begin{align*}
& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
\end{align*}
Here $\varepsilon_i$ is the sign of $i$.
In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
\begin{align*}
& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
\end{align*}

>>>>

The action of $x_\alpha(\xi)$ can be visualized on a weight diagram of $\pi$ as follows. Blah-blah-blah
%\textbf{TODO: Write a passage about this}

@@

Although it is possible to fix signs of the action constants in the statement of \cref{lemma:Matsumoto} (see~\cite{V08}), we make no attempt to do this in this article.

Let $\lambda_1, \lambda_2 \in \Lambda(\pi)$ be a pair of weights of a representation $\pi$ such that $\lambda_1-\lambda_2\in \Phi$.
It will be convenient for us to write $x_{\lambda_1,\lambda_2}(\xi)$ instead of $x_{\lambda_1-\lambda_2}(\xi)$.
For example, for $\Phi=\rA_\ell$ we have $x_{1,2}(\xi)=x_{1-2}(\xi)=x_{\varpi_1 - \varpi_1 + \alpha_1}(\xi) = x_{\alpha_1}(\xi)$.

%\begin{rem}
%For classical groups there is a standard way to fix the signs.
%In case $\Phi=\rC_\ell$ the long and short root unipotents are
%\begin{align*}
%& x_{i,-i}(\xi)=e+\xi e_{i,-i}, \\ 
%& x_{i,j}(\xi)=e+\xi e_{ij}-\varepsilon_i\varepsilon_j\xi e_{-j,-i},\quad i\neq\pm j.
%\end{align*}
%Here $\varepsilon_i$ is the sign of $i$.
%In case $\Phi=\rB_\ell,\rD_\ell$ the long and short root unipotents in $\SO(n,R)$ are
%\begin{align*}
%& x_{i,j}(\xi)=e+\xi e_{ij}-\xi e_{-j,-i},\quad i\neq\pm j,\ i,j\neq0, \\
%& x_{i0}(\xi)=e+2\xi e_{i0}-\xi e_{0,i}-\xi^2 e_{i,-i},\quad i\neq0.
%\end{align*}
